### 2017-03-31 paper/modes.tex
pass on section II

The configuration \Seq{} is a proper fit for short-running test suites
since this is the default configuration and the execution provides
feedback in an acceptable time. However, for costly suites, it is
impractical for developers to wait long-running executions to take
action.  In this scenario, the remaining configuration may help to
amortize the execution cost depending on how the test suite was
designed. For instance, the configuration \SeqClassParMeth{} may
speedup the execution of test suites composed large test classes since
the cost of running all test methods is amortized by a pool of
threads. Similarly, the configuration \ParClassSeqMeth{} may speedup
test suites composed by several small test classes. Notice that both
configurations \ParClassSeqMeth{} and \SeqClassParMeth{} avoid
data-race condition at different levels. For instance, if two test
classes performs I/O operations to the same file, the configuration
\SeqClassParMeth{} would be preferable. Finally, the configuration
\ParClassParMeth{} does not impose any sequential execution but it is
more likely to manifest data-races as methods from different classes
run in parallel.

>>>>

The configuration \Seq{} is a proper fit for short-running test suites
since this is the default configuration and the execution provides
feedback in an acceptable time. However, for costly suites, it is
impractical for developers to wait long-running executions to take
action.  In this scenario, the remaining configuration may help to
amortize the execution cost depending on how the test suite was
designed. For instance, the configuration \SeqClassParMeth{} may
speedup the execution of test suites composed large test classes since
the cost of running all test methods is amortized by a pool of
threads. Similarly, the configuration \ParClassSeqMeth{} may speedup
test suites composed by several small test classes. Notice that both
configurations \ParClassSeqMeth{} and \SeqClassParMeth{} avoid
data-race condition at different levels. \Luis{This is wrong $\rightarrow$} 
For instance, if two test classes performs I/O operations to the same file,
the configuration \SeqClassParMeth{} would be preferable. Finally, 
the configuration \ParClassParMeth{} does not impose any sequential 
execution but it is more likely to manifest data-races as methods 
from different classes run in parallel.
